Identification of high-yielding soybean lines with exceptional seed composition qualities

### 2022-05-10 doc/manuscript/manuscript.Rmd
Cleaned up the targets file a bit and saved some small changes to the main manuscript document

Multiple RILs in each test were identified with yield comparable to, or superior to that of the check cultivars included in each test.

>>>>

Several RILs in each of the tests had yield that was comparable to that of their check cultivars. This was determined both quanititatively through the use of contrasts between the mean of each RIL with the average of the yield check means, and qualitatively by inspecting the standard errors on the estimation of the genotype marginal means for yield. Among these genotypes with yield comparable to that of the check cultivars were several genotypes with
